A Wait-free Queue with Polylogarithmic Step Complexity

### 2023-01-09 podc_paper/correctness-2.tex
working on gc invariant

The correctness of \op{GetEnqueue} and \op{indexDequeue}, which are identical to the original version of the implementation are dependent only on the fact that we do not discard blocks needed by those routines.
The following lemmas show this.

>>>>

\subsubsection{GC Keeps Needed Blocks}

The correctness of \op{GetEnqueue} and \op{indexDequeue}, which are very similar to the 
original implementation, are dependent only on the fact that GC does not 
discard blocks needed by those routines.
The following lemmas are used to show this.

We say a block is \emph{finished} if 
\begin{itemize}
\item
it has been propagated to the root,
\item
the value of each enqueue contained in the block has either been returned by a dequeue
or written in the \fld{result} field of a dequeue, and
\item
each dequeue contained in the block has either terminated or has a non-null \fld{result} field in the leaf block that represents it.
\end{itemize}
Intuitively, once a block is finished, operations no longer need to pass through the block
to compute responses to operations.
The following is an immediate consequence of the definition of finished and what it means for an operation to be contained in a block.

\begin{observation}\label{subblocksFinished}
A block is finished if and only all of its subblocks are finished.
\end{observation}

\begin{invariant}
If the minimum \fld{index} of any block in \vv's RBT is $b_{min}$, then
all blocks that were ever added to \vv\ with $\fld{index}$ at most $b_{min}$ are finished.
\end{invariant}
\begin{proof}
The invariant is true initially, since the minimum \fld{index} block in \vv's RBT is the empty block, which is (vacuously) finished.

We must show the invariant is preserved whenever $\vv.\fld{blocks}$ changes.
The minimum \fld{index} of \vv's RBT can only change when \vv's RBT changes, either at line 
\ref{appendLeafGC} (if \vv\ is a leaf) or at line \ref{casGC} (if \vv\ is an internal node).
In either case, the step changes $\vv.\fld{blocks}$ is changed
from $T$ to $T'$, where $T'$ is obtained by  a call to \op{AddBlock}(\vv, $T$, $B$).
(In the case of a leaf \vv, this is true because only the process that owns the leaf ever
writes to $\vv.\fld{blocks}$.)
If the \op{AddBlock} does not do GC (lines \ref{GCstart}--\ref{GCend}), 
then $T'$ is obtained by adding a new block to $T$, so by \Cref{} the minimum \fld{index}
is the same.
So consider the case where the \op{AddBlock} performs GC.
We must show that any block of \vv\ whose index is less than or equal to the
minimum \fld{index} in $T'$ is finished when $T'$ is installed in $\vv.\fld{blocks}$.
Since $T'$ is obtained by discarding all blocks with \fld{index} at most $s$ (and adding
a block with a larger index), it suffices to show that all blocks that were ever added
to \vv's RBT with \fld{index} at most $s$ are finished.

\here{to be continued}
might need assn that ops so far are consistent with L

Claim:  After an \op{AddBlock} finishes its call to \op{Help} on line \ref{invokeHelp}
all blocks of $v$ with \fld{index} less than or equal to $s$ are finished.
